The Iterative Signature Algorithm

### 2009-04-30 isa/inst/doc/ISA_tutorial.Rnw
isa: added a method to convert ISA modules to Biclust objects from the biclust package.

Finally, let us take a look at some of the other modules, that were
also kept after the robustness-based filtering. Here we plot nine of
them.
<<othermods.pre>>=
png("othermods.png", 800, 800)
@ 
<<othermods>>=
othermods <- which(modules3$seeddata$rob < 27.5)[1:5]
print(plot.modules(modules3, othermods, data=data[[1]]))
@ 
<<othermods.post>>=
dev.off()
@

@@

<<sensbox,include=FALSE,results=hide>>=
boxplot(best, names=noise, xlab="Noise level", ylab="Sensitivity",
        cex.lab=1.5)
@
\begin{figure}
\centering
<<sensbox2,fig=TRUE,echo=FALSE,results=hide,width=10,height=5>>=
<<sensbox>>
@ 
\caption{The sensitivity of the ISA in the function of noise. The
  sensitivity score is calculated by finding the best (in terms of
  Pearson correlation) ISA module for each block in the input matrix.

  ISA is very sensitive to relatively large noise levels.
}
\label{fig:sensbox}
\end{figure}

To test the specificity, we create boxplots for the correlation
coefficients of all modules found by ISA and their closest real
module.
<<spec>>=
spec <- lapply(seq_along(modules), function(i) {
  cc <- pmin(cor(modules[[i]]$rows != 0, data[[i]][[2]]),
             cor(modules[[i]]$columns != 0, data[[i]][[3]]))
  apply(cc, 1, max)
})
@ 
<<specbox,include=FALSE,results=hide>>=
boxplot(spec, names=noise, xlab="Noise level", ylab="Specificity",
        cex.lab=1.5)
@
\begin{figure}
\centering
<<specbox2,fig=TRUE,echo=FALSE,results=hide,width=10,height=5>>=
<<specbox>>
@
\caption{Specificity of the ISA modules, in the function of
  noise. Specificity was calculated by finding the best -- again,
  by highest Pearson correlation -- matching block in the input matrix
  for each ISA module. These correlation coefficients are plotted in a
  boxplot for each noise level.

  Specificity for ISA decreases approximately linearly with the
  increase of noise.
}
\label{fig:specbox}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{overlapplot}
\caption{The input matrix with two overlapping blocks and the ISA
  modules for this data set. The first three modules were found at
  milder threshold parameters, that is why they are bigger. As you can
  see for Modules #1 and #2, at milder thresholds there is a higher
  probability that ISA will pick up some incorrect rows/columns.
}
\label{fig:overlapplot}
\end{figure}

>>>>

Finally, let us take a look at some of the other modules, that were
also kept after the robustness-based filtering. Here we plot nine of
them.
<<othermods.pre,echo=FALSE,results=hide>>=
png("othermods.png", 800, 800)
@ 
<<othermods>>=
othermods <- which(modules3$seeddata$rob < 27.5)[1:5]
print(plot.modules(modules3, othermods, data=data[[1]]))
@ 
<<othermods.post,echo=FALSE,results=hide>>=
dev.off()
@

@@

<<sensbox,include=FALSE,results=hide>>=
boxplot(best, names=noise, xlab="Noise level", ylab="Sensitivity",
        cex.lab=1.5)
@
\begin{figure}
\centering
<<sensbox2,fig=TRUE,echo=FALSE,results=hide,width=10,height=5>>=
<<sensbox>>
@ 
\caption{The sensitivity of the ISA in the function of noise. The
  sensitivity score is calculated by finding the best (in terms of
  Pearson correlation) ISA module for each block in the input matrix.
  ISA is very sensitive to relatively large noise levels.
}
\label{fig:sensbox}
\end{figure}

To test the specificity, we create boxplots for the correlation
coefficients of all modules found by ISA and their closest real
module.
<<spec>>=
spec <- lapply(seq_along(modules), function(i) {
  cc <- pmin(cor(modules[[i]]$rows != 0, data[[i]][[2]]),
             cor(modules[[i]]$columns != 0, data[[i]][[3]]))
  apply(cc, 1, max)
})
@ 
<<specbox,include=FALSE,results=hide>>=
boxplot(spec, names=noise, xlab="Noise level", ylab="Specificity",
        cex.lab=1.5)
@
\begin{figure}
\centering
<<specbox2,fig=TRUE,echo=FALSE,results=hide,width=10,height=5>>=
<<specbox>>
@
\caption{Specificity of the ISA modules, in the function of
  noise. Specificity was calculated by finding the best -- again,
  by highest Pearson correlation -- matching block in the input matrix
  for each ISA module. These correlation coefficients are plotted in a
  boxplot for each noise level.
  Specificity of ISA decreases approximately linearly with the
  increase of noise.
}
\label{fig:specbox}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{overlapplot}
\caption{The input matrix with two overlapping blocks and the ISA
  modules for this data set. The first three modules were found at
  milder threshold parameters, that is why they are bigger. As you can
  see for Modules \#1 and \#2, at milder thresholds there is a higher
  probability that ISA will pick up some incorrect rows/columns.
}
\label{fig:overlapplot}
\end{figure}
